%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Profile}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
% \cvsubsection{Service and Outreach}
% \begin{cvhonors}
% %---------------------------------------------------------
%   \cvhonor
%     {Science Fair} % Event/Organization
%     {Volunteer Judge} % Position
%     {} % Location
%     {2018} % Date(s)
    
% %---------------------------------------------------------
%   \cvhonor
%     {Graduate Student Association} % Event/Organization
%     {Committee Member} % Position
%     {} % Location
%     {2016-2017} % Date(s)
    
% \end{cvhonors}

\cvsubsection{Research interests}

\begin{cvpubs}
    \cvpub{\textbf{State-space models}, computation of filtering distribution, smoothing distribution and likelihood in state-space models; their application to real data; development of approximate and scalable methods for high-dimensional scenarios; composite likelihood. }
    
    \cvpub{\textbf{Machine Learning \slash Deep Learning}, development and training of deep neural networks in both frequentist and Bayesian frameworks; development and training of machine learning algorithms in both supervised and unsupervised learning scenarios with a focus on engineering applications (e.g. tunneling).}
    
    \cvpub{\textbf{Monte Carlo}, implementation and theoretical properties of Monte Carlo algorithms, with a particular focus on Sequential Monte Carlo and the construction of smart proposal distributions and resampling schemes.}
    
    \cvpub{\textbf{Epidemiology}, use of compartmental models in epidemiology and the challenge of performing inference in complicated scenarios (e.g. individual-based models).}
\end{cvpubs}

\cvsubsection{Coding skills}

\begin{cvpubs}
    \cvpub{\textbf{Operating system}, advanced knowledge of Windows and Linux (e.g. Ubuntu, Fedora).}
    
    \cvpub{\textbf{Programming Languages}, advanced knowledge of Python; good knowledge of R, MATLAB, C \slash C++.}\\
    \cvpub{\textbf{Python}: state-space modelling with Numpy, JAX and TensorFlow; development of inference algorithms (e.g. EM, MCMC, SMC$^2$) using Numpy, JAX and TensorFlow; Machine Learning using scikit-learn; Deep Learning using PyTorch and TensorFlow; database management using pandas; graph operations using NetworkX; GPU computations and automatic differentiation with JAX, PyTorch and TensorFlow.}
    
    \cvpub{\textbf{Others}, High-performance computing with PBS and SLURM; SQL; Git and version control; \LaTeX; Microsoft Office.}
\end{cvpubs}

\cvsubsection{Development}

\begin{cvpubs}
    \cvpub{Autumn 2020. \textbf{Deep Learning Specialization}, 5 courses on deep learning with assessments to learn about neural networks (e.g. CNN, RNN, LSTM), regularization techniques (e.g. DropOut) and implementation using Python (e.g. TensorFlow). coursera.}
\end{cvpubs}

\cvsubsection{Languages}
\begin{small} \color{black}

\vspace{-0.125cm}
\begin{itemize}
    \item Italian (spoken and written)
    \item English (spoken and written)
\end{itemize}
\end{small}

% \cvsubsection{Professional Memberships}

% \begin{small} \color{black}
% One fancy society \\
% Another fancy society \\
% \end{small}
