%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
% \vspace{-0.3cm}
% \begin{small}\textit{* presenting author; \textsuperscript{+} mentored undergraduate}\end{small}


%-------------------------------------------------------------------------------
\cvsubsection{Invited Presentations}
%-------------------------------------------------------------------------------

\begin{cvpubs}
    
    \cvpub {Dec. 2024. \textit{Consistent and fast inference in compartmental models of epidemics using Poisson Approximate Likelihoods}. Invited talk at the \href{https://www.cmstatistics.org/CFECMStatistics2024/submission.php}{``Advances in Bayesian methods'' session of CMStatistics 2024}. London, UK.}
    
    \cvpub {Jun. 2024. \textit{Consistent and fast inference in compartmental models of epidemics using Poisson Approximate Likelihoods}. Invited talk at the \href{https://www.usi.ch/en/feeds/25999}{Satellite workshop to International Society for Bayesian Analysis (ISBA) world meeting}. Lugano, Switzerland.}

    \cvpub {Mar. 2023. \textit{Approximating optimal SMC proposal distributions in individual-based epidemic models}. Invited talk at the \href{https://bayescomp2023.com/}{Satellite event of BayesComp2023}. Levi, Finland.} 
    
    \cvpub {Mar. 2023. {\textit{Approximating optimal SMC proposal distributions in individual-based epidemic models}}. Invited talk at the \href{https://www.lancaster.ac.uk/bayes-for-health/b4h-workshops/workshop-2023/}{Bayes4Health annual workshop} at the University of Oxford. Oxford, UK.}
    
    \cvpub {Jun. 2022. \textit{Exploiting locality in high-dimensional factorial hidden Markov models}. Invited talk at the \href{http://isbis2022.dii.unina.it/}{ISBIS Conference 2022}. Naples, Italy.}    
     
    \cvpub {Mar. 2022. \textit{Inference on Extended-Spectrum Beta-Lactamase Escherichia coli and Klebsiella pneumoniae data through SMC$^2$}. Invited talk at the \href{https://www.drumconsortium.org/}{DRUM} Stakeholder meeting. Lilongwe, Malawi.}
    
    \cvpub {Sept. 2021. {\textit{Exploiting locality in high-dimensional factorial hidden Markov models}}. Presentation for the \href{https://www.lancaster.ac.uk/bayes-for-health/b4h-workshops/workshop-2021/}{Bayes4Health annual workshop} at the University of Cambridge. Cambridge, UK.}
    
\end{cvpubs}


%-------------------------------------------------------------------------------
\cvsubsection{Contributed Presentations}
%-------------------------------------------------------------------------------

\begin{cvpubs}
    
     \cvpub {Jul. 2024. \textit{Simulation Based Composite Likelihood}. Presentation for the conference \href{https://unive.it/web/en/2208/home}{ISBA 2024} in the Multi-track session 4F ``Simulation-Based inference''. Venice, IT.}
    
     \cvpub {Oct. 2023. \textit{Lecture on parallel computing for epidemiological modelling}. Lecture for the \href{https://www.lancaster.ac.uk/bayes-for-health/news/masterclass-in-parallel-computing}{Parallel computing masterclass} at Lancaster University. Lancaster, UK.}
     
    \cvpub {Sept. 2023. \textit{Simulation Based Composite Likelihood}. Presentation for the conference \href{https://iddconf.org/}{IDDconf2023}. Ambleside, UK.} 
    
     \cvpub {Apr. 2022. \textit{Lecture on the SMC$^2$ algorithm}. Lecture for the \href{https://www.lancaster.ac.uk/bayes-for-health/news/joine-bayes4health-and-cosines-masterclass}{Sequential Monte Carlo masterclass} at the University of Bristol. Bristol, UK.}
   
    \cvpub {Dec. 2022. {\textit{Approximating optimal SMC proposal distributions in individual-based epidemic models}}. Presentation for the \href{https://sites.google.com/site/welcomehomeunito/welcome-home-2022}{Welcome Home 2022} workshop at Università degli studi di Torino. Torino, Italy.}
    
    \cvpub {Dec. 2021. {\textit{Inference on Extended-Spectrum Beta-Lactamase Escherichia coli and Klebsiella pneumoniae data through SMC$^2$}}. Presentation for the \href{https://sites.google.com/site/welcomehomeunito/welcome-home-2021?authuser=0}{Welcome Home 2021} workshop at Università degli studi di Torino. Torino, Italy.}
        
    \cvpub {Dec. 2020. \textit{Inference in Stochastic Epidemic Models via Multinomial Approximations}. Presentation for the \href{https://sites.google.com/site/welcomehomeunito/welcome-home-2020?authuser=0}{Welcome Home 2020} workshop at Università degli studi di Torino. Torino, Italy.}
    
\end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{Seminars}
%-------------------------------------------------------------------------------

\begin{cvpubs}
    \cvpub {Mar. 2024. \textit{Consistent and fast inference in compartmental models of epidemics using Poisson Approximate Likelihoods}. Seminar at \href{https://www.nottingham.ac.uk/}{University of Nottingham} (School of Mathematical Sciences). Nottingham, UK.} 
    
    \cvpub {Dec. 2023. \textit{Consistent and fast inference in compartmental models of epidemics using Poisson Approximate Likelihoods}. Seminar at \href{https://www.durham.ac.uk/}{Durham University} (Department of Mathematical Sciences). Durham, UK.} 
    
    \cvpub {Nov. 2023. \textit{Mini-Workshop on Epidemiological Modeling}. A 3h \href{https://math.upd.edu.ph/2023/10/mini-workshop-on-epidemiological-modeling}{workshop} at the University of the Philippines Diliman (Institute of Mathematics). Manila, Philippines.}     
    
    \cvpub {Sep. 2023. \textit{Inference in stochastic compartmental models: a Pharmacokinetics and Epidemiology perspective}. Seminar at the Università della Svizzera italiana (Faculty of Biomedical Sciences). Online.} 
    
    \cvpub {Feb. 2022. \href{https://www.youtube.com/watch?v=WHVvWJVrTbE}{\textit{Inference on Extended-Spectrum Beta-Lactamase Escherichia coli and Klebsiella pneumoniae data through SMC$^2$}}. Seminar for the Bayes4Health and CoSInES grants seminars series. Online.}
    
    \cvpub {Apr. 2022. \textit{Inference on Extended-Spectrum Beta-Lactamase Escherichia coli and Klebsiella pneumoniae data through SMC$^2$}. Seminar at the University of Padova (Department of Statistics). Padova, Italy.}
    
    \cvpub {Dec. 2021. {\textit{Inference in Stochastic Epidemic Models via Multinomial Approximations}}. Seminar at the Postgraduate seminars series of Lancaster University (Department of Mathematics and Statistics). Online.}
        
    \cvpub {Apr. 2021. \href{https://youtu.be/fmbqkF0na3M}{\textit{Inference in Stochastic Epidemic Models via Multinomial Approximations}}. Seminar for the Bayes4Health and CoSInES grants seminars series. Online.}
    
    \cvpub {Sept. 2019. \textit{Exploiting locality in high-dimensional factorial hidden Markov models}. Seminar at the University of Bristol (Institute for Statistical Science). Bristol, UK.}
    
\end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{Poster Presentations}
%-------------------------------------------------------------------------------

\begin{cvpubs}

    \cvpub {Jul. 2024. \textit{Simulation Based Composite Likelihood}. Poster presentation at  \href{https://unive.it/web/en/2208/home}{ISBA 2024}. Venice, IT.} 

    \cvpub {Jul. 2023. \textit{Exploiting locality in high-dimensional Factorial hidden Markov models}. Poster presentation at  \href{https://www.gresearch.com/}{G-Research}. London, UK.} 

    \cvpub {Jul. 2023. \textit{Exploiting locality in high-dimensional Factorial hidden Markov models}. \href{https://icml.cc/virtual/2023/papers.html?filter=titles&search=Exploiting+locality+in+high-dimensional+Factorial+hidden+Markov+models}{Poster presentation at the ICML2023 conference}. Online.} 
 
    \cvpub {Mar. 2021. {\textit{Inference in Stochastic Epidemic Models via Multinomial Approximations}}. \href{https://virtual.aistats.org/virtual/2021/poster/1661}{Poster presentation at the AISTAT2021 conference}. Online.}
\end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{Reading group Presentations}
%-------------------------------------------------------------------------------

\begin{cvpubs}

    \cvpub {Feb. 2024. \textit{A State-Space Perspective on Modelling and Inference for Online Skill Rating}. Presentation for the \href{https://lu-csml.github.io/}{CSML} reading group at Lancaster University (Department of Mathematics and Statistics). Lancaster, UK.}

    \cvpub {Nov. 2023. \textit{Simulation Based Composite Likelihood}. Presentation for the \href{https://lu-csml.github.io/}{CSML} reading group at Lancaster University (Department of Mathematics and Statistics). Lancaster, UK.}
    
    \cvpub {May 2023. {\textit{Localised filtering algorithm: the BPF and the Graph Filter}}. Presentation for the \href{https://lu-csml.github.io/}{CSML} reading group at Lancaster University (Department of Mathematics and Statistics). Lancaster, UK.}
    
    \cvpub {Sept. 2022. {\textit{Inference in Stochastic Epidemic Models via Multinomial Approximations}}. Presentation for the \href{https://lu-csml.github.io/}{CSML} reading group at Lancaster University (Department of Mathematics and Statistics). Lancaster, UK.}
    
    \cvpub {Nov. 2021. {\textit{Inference on Extended-Spectrum Beta-Lactamase Escherichia coli and Klebsiella pneumoniae data through SMC$^2$}}. Presentation for the LURGiE reading group at Lancaster University (Department of Mathematics and Statistics). Lancaster, UK.}
  
    \cvpub {May 2021. \textit{Dynamic Bayesian Neural Network}. Presentation for the \href{https://lu-csml.github.io/}{CSML} reading group at Lancaster University (Department of Mathematics and Statistics). Lancaster, UK.}

    \cvpub {Mar. 2021. \textit{Build Bayesian Neural Network in Pytorch}. Presentation for the \href{https://github.com/LorenzoRimella/Build_Bayesian_NN_with_Pytorch}{JAX} reading group at Lancaster University (Department of Mathematics and Statistics). Lancaster, UK.}

\end{cvpubs}