%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\cvsubsection{Articles in Peer-Reviewed Journals}
%---------------------------------------------------------

\begin{cvpubs}
    \cvpub{\textbf{Rimella L}, Jewell C, Fearnhead P. 2025. Simulation Based Composite Likelihood. To appear in  \href{https://link.springer.com/journal/11222}{Statistics and Computing} (\href{https://arxiv.org/abs/2310.10761}{arXiv:2310.10761 [stat.ME]}).}
    
    \cvpub{Rimella N, \textbf{Rimella L}, Osello A. 2025. Machine Learning Method for As-Is Tunnels Information Model Reconstruction. \href{https://www.sciencedirect.com/science/article/pii/S0926580525000792}{Automation in Construction}.}
    
    \cvpub{\textbf{Rimella L}, Whiteley N. 2025. Hidden Markov Neural Networks. \href{https://www.mdpi.com/1099-4300/27/2/168}{Entropy}.}
 
    \cvpub{Duffield S, Power S, \textbf{Rimella L}. 2024. A State-Space Perspective on Modelling and Inference for Online Skill Rating. \href{https://academic.oup.com/jrsssc/advance-article/doi/10.1093/jrsssc/qlae035/7734616}{Journal of the Royal Statistical Society: Series C}.}

    \cvpub{Mwapasa T, Chidziwisano K, Mphasa M, Cocker D, \textbf{Rimella L}, Amos S, Feasey N, Morse T. 2024. Key environmental exposure pathways to antimicrobial resistant bacteria in southern Malawi: A SaniPath approach.	\href{https://www.sciencedirect.com/science/article/pii/S0048969724042906}{Science of the Total Environment}}

    \cvpub{Whitehouse M, Whiteley N, \textbf{Rimella L}. 2023. Consistent and fast inference in compartmental models of epidemics using Poisson Approximate Likelihoods. \href{https://academic.oup.com/jrsssb/advance-article/doi/10.1093/jrsssb/qkad065/7218445}{Journal of the Royal Statistical Society: Series B}.}

    \cvpub{\textbf{Rimella L}, Jewell C, Fearnhead P. 2023. Inference on Extended-Spectrum Beta-Lactamase \emph{Escherichia coli} and \emph{Klebsiella pneumoniae} data through $SMC^2$.	\href{https://academic.oup.com/jrsssc/advance-article/doi/10.1093/jrsssc/qlad055/7219386}{Journal of the Royal Statistical Society: Series C}.}
    
    \cvpub{\textbf{Rimella L}, Jewell C, Fearnhead P. 2023. Approximating optimal SMC proposal distributions in individual-based epidemic models. \href{https://www3.stat.sinica.edu.tw/preprint/SS-2022-0198_Preprint.pdf}{Statistica Sinica}.}

    \cvpub{\textbf{Rimella L}, Whiteley N. 2022. Exploiting locality in high-dimensional factorial hidden Markov models. \href{https://www.jmlr.org/papers/volume23/19-267/19-267.pdf}{Journal of Machine Learning Research}.}
    
\end{cvpubs}

%---------------------------------------------------------
\cvsubsection{International Conference Proceedings (Peer-Reviewed)}
%---------------------------------------------------------

\begin{cvpubs}

	\cvpub{Whiteley N, \textbf{Rimella L}. 2021. Inference in Stochastic Epidemic Models via Multinomial Approximations. \href{http://proceedings.mlr.press/v130/whiteley21a.html}{International Conference on Artificial Intelligence and Statistics, 1297-1305}.}
	
\end{cvpubs}

% %---------------------------------------------------------
\cvsubsection{Preprints and Submitted Articles}
% %---------------------------------------------------------

\begin{cvpubs}

	\cvpub{\textbf{Rimella L}, Whiteley N, Jewell C, Fearnhead P, Whitehouse M. 2025. Scalable calibration for partially observed individual-based epidemic models through categorical approximations. Arxiv paper (\href{https://arxiv.org/abs/2501.03950}{arXiv:2501.03950 [stat.ME]}).}
 
	\cvpub{Battiston M, \textbf{Rimella L}. 2024. Disclosure risk assessment with Bayesian non-parametric hierarchical modelling. Submitted (\href{https://arxiv.org/pdf/2408.12521}{arXiv:2408.12521 [stat.AP]}).}
\end{cvpubs}


% %---------------------------------------------------------
\cvsubsection{Open-source Softwares}

\begin{cvpubs}

	\cvpub{\textbf{Rimella L}. 2025. CAL: \href{https://github.com/LorenzoRimella/CAL}{https://github.com/LorenzoRimella/CAL}.}

	\cvpub{Rimella N, \textbf{Rimella L}. 2024. ML\_tunneling: \href{https://github.com/LorenzoRimella/ML_tunneling}{https://github.com/LorenzoRimella/ML\_tunneling}.}
 
	\cvpub{\textbf{Rimella L}. 2024. BNP\_DR: \href{https://github.com/LorenzoRimella/BNP\_DR}{https://github.com/LorenzoRimella/BNP\_DR}.}
 
	\cvpub{Duffield S, \textbf{Rimella L}. 2024. abile: \href{https://github.com/SamDuffield/abile}{https://github.com/SamDuffield/abile}.}
  
	\cvpub{\textbf{Rimella L}. 2023. SimBa-CL: \href{https://github.com/LorenzoRimella/SimBa-CL}{https://github.com/LorenzoRimella/SimBa-CL}.}
 
	\cvpub{Whitehouse M, \textbf{Rimella L}. 2023. PAL: \href{https://github.com/LorenzoRimella/PAL}{https://github.com/LorenzoRimella/PAL}.}
 
	\cvpub{\textbf{Rimella L}. 2022. SMC2-ILM: \href{https://github.com/LorenzoRimella/SMC2-ILM}{https://github.com/LorenzoRimella/SMC2-ILM}.}
 
	\cvpub{\textbf{Rimella L}. 2022. Optimal\_IBM\_proposal: \href{https://github.com/LorenzoRimella/Optimal_IBM_proposal}{https://github.com/LorenzoRimella/Optimal\_IBM\_proposal}.}
 
	\cvpub{\textbf{Rimella L}. 2021. GraphFilter-GraphSmoother: \href{https://github.com/LorenzoRimella/GraphFilter-GraphSmoother}{https://github.com/LorenzoRimella/GraphFilter-GraphSmoother}.}
 
	\cvpub{\textbf{Rimella L}. 2020. HiddenMarkovNeuralNetwork: \href{https://github.com/LorenzoRimella/HiddenMarkovNeuralNetwork}{https://github.com/LorenzoRimella/HiddenMarkovNeuralNetwork}.}
 
	\cvpub{\textbf{Rimella L}. 2020. Multinomial-Approximations-for-compartmental-models: \href{https://github.com/LorenzoRimella/Multinomial-Approximations-for-compartmental-models}{https://github.com/LorenzoRimella/Multinomial-Approximations-for-compartmental-models}.}

\end{cvpubs}

% %---------------------------------------------------------

% % %---------------------------------------------------------
% \cvsubsection{In Prep}
% % %---------------------------------------------------------

% \begin{cvpubs}
% \small \color{black}

% \end{cvpubs}

% % %---------------------------------------------------------
